Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-13 proposal/mprop.tex
Add some work on proposed approach

The main research question this study is trying to answer is 
what makes for a valuable, high quality?

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey}
% 10 - 12 pages

@@

\subsection{Data Quality and Metrics}

@@

\subsection{Issue Quality}

@@

\subsection{Measuring Cost and Waste in Software Projects}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Approach}

% 3- 4 pages

What are we actually going to do?

\textbf{Research Questions}:
\begin{itemize}
  \item what makes for a quality software ticket that could help developers
    fix the bug/implement the feature faster?
  \item what can be changed in software ticket structure that could ease writing
    such quality software tickets (e.g. add specific fields to the ticket in
    Jira, add instructions as comments on how reporters should write such a 
    ticket)?
  \end{itemize}

\textbf{Experimental design}: conduct a statistical analysis over popular 
open source projects such as Mozilla or Apache and extract tickets via 
some API (maybe REST based). Then, define what makes for 2 similar tickets
(maybe look at story points assigned by experienced triagers; probably we also
need to use only severe/critical ones as they will probably be fixed first
and there will not be any delay, such as waiting for the main developer to come
back from vacation) and then see how much time it took both to be completed
so that we can infer what differences did those 2 tickets have (and see if, for
example, stack traces influenced the duration of the ticket).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Plan}

>>>>

The main research question this study is trying to answer is 
what makes for a valuable, high quality ticket?

@@

The rest of this project proposal is structured as follows:
  \begin{itemize}
    \item Section \ref{background_survey} presents both the study design 
      and the background survey, which in turn is divided into three 
      subsection:
        \begin{itemize}
          \item subsection \ref{data_quality} describes the literature
            review on data quality and metrics;
          \item subsection \ref{issue_quality} describes the background
            survey on issue/ticket quality;
          \item subsection \ref{waste} elicits literature on 
            waste in software projects;
        \end{itemize}
    \item Section \ref{proposed_approach} describes how we would like 
      to conduct the research;
    \item Section \ref{work_plan} shows how we broke down the work
      so that we keep a consistent pace throughout the lifecycle of 
      the research.
  \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey}\label{background_survey}
% 10 - 12 pages

@@

\subsection{Data Quality and Metrics}\label{data_quality}

@@

\subsection{Issue Quality}\label{issue_quality}

@@

\subsection{Measuring Cost and Waste in Software Projects}\label{waste}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Approach}\label{proposed_approach}

\subsection{Experimental Design}

We would like to begin the research by conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the final list of projects
will be finalized once some tests will be run. Then, define what makes for 2 similar tickets
(maybe look at story points assigned by experienced triagers; probably we also
need to use only severe/critical ones as they will probably be fixed first
and there will not be any delay, such as waiting for the main developer to come
back from vacation) and then see how much time it took both to be completed
so that we can infer what differences did those 2 tickets have (and see if, for
example, stack traces influenced the duration of the ticket).

\subsection{Variables Tested}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Plan}\label{work_plan}
